
\section*{Sources of information}


Some material (handouts, slides) which have been presented during the
course) or circulated via the email list.



\begin{tabular}{r@{\quad\quad}rll}
  \hline
  1. & 19. October & coma  & 
  \href{slides/main-coma.pdf}{slides}
  \\
  2. & 19. October & cvs (obsolete) & \href{handouts/handout1.pdf}{handout 1}
  \\
  3. & 9. November & subversion + some tool remarks &
  \href{handouts/handout2.pdf}{handout 2}
  \\
   & 16. November & bugzilla &
  \href{handouts/handout3.pdf}{handout 3}
  \\
   & 15. November & groups &
  \href{handouts/handout4.pdf}{organizational form}
  \\
   & 15. November & groups and next steps &
  \href{handouts/handout5.pdf}{handout 5}
  \\\hline 
   & 18. November &  &
  \href{spec/v2/main.pdf}{data spec} (v2)
  \\\hline 
   & 30. November &  &
  \href{handouts/handout6.pdf}{communication problems}
  \\
   & 31. Januar &  &
  \href{handouts/handout7.pdf}{E-O-S demo}
  \\
\end{tabular}




\begin{description}
\item[BB]
  \href{http://snert.informatik.uni-kiel.de:8080/~swprakt/phpBB2/}{bulletin
    board}: not obligatory, but perhaps useful.
\item[Bugzilla] 
  \href{http://snert.informatik.uni-kiel.de:8080/~swprakt/bugzilla}{bugzilla}: 
  login via email-address + your chosen password (not the generated one, not the ssh-passphrase)
  For some hints, see also handout 3.
\item[Repository:] The repository resides on the \texttt{snert}-machine.
  Write-access is password-protected, for browsing the current status, you
  can click here
  \href{http://snert.informatik.uni-kiel.de:8080/svn/coma/}{\textbf{current
      repository status}}. Write access is granular in the following sense:
  each group can write only within its own domain of responsibilities.
\item[examples:] some examples you can use for inspiration
  \begin{itemize}
  \item a \href{requirements/examples/cfpapers.html}{ ``call-for-papers''}
    to have a look how a conference advertisement for authors could look
    like.
  \item an empty \href{requirements/examples/reviewform.txt}{ascii review
      form} for some conference
  \end{itemize}
\end{description}




\input{meetings}





\subsection*{Spec + tools groups}
\label{sec:material.spec-tools}%

The following is the material worked out in the first phase. It is also
checked in under \texttt{spec/material} in the main trunk of the
development.


\begin{tabular}{llll}
  14.11 & Spec 1 & 
  \href{spec/material/spec1/spezifikation.pdf}{specification}, 
  \href{spec/material/spec1/slides.pdf}{coma slides}, 
  & (in German)
  \\
  16.11 & Spec 2 & 
  \href{spec/material/spec2/usecase.pdf}{usecase}, 
  \href{spec/material/spec2/datenstruktur.ps}{Datenstruktur}, 
  \href{spec/material/spec2/slides.pdf}{coma slides}
  & (in German)
  \\
  10.11 & Alexander & \href{spec/material/derenbach/tools.pdf}{choice of tools}
  \\
  ?  & Tools 1 & \href{spec/material/tools1/tools.txt}{choice of tools}
  \\
  15.11.04 & Tools 2 &
  \href{spec/material/tools2/tools.pdf}{choice of tools}
  \\
  16.11 & Tools 3 & \href{spec/material/tools3/tools.pdf}{choice of tools}
  \\
  - & Tests & \href{spec/material/tests/tests.txt}{Test concept}
\end{tabular}




\subsubsection*{Other stuff}

\begin{tabular}[t]{lp{8cm}}
 \LaTeX\ \href{misc/handout.cls}{handout class}  (+
 \href{misc/hevea.sty}{hevea}) & for tex'ing the handouts, if wished. hevea is only needed if 
 you want to generate webpages out of it, i.e., if the switch \textrm{\webtrue} is set
\end{tabular}


\subsection*{Tools potpourri \& matrix}

The following gives a short overview over the tools, languages \ldots
needed for the project. The are classified according to the differnt
developer grouds and the targeted users.

Entries $+$ mean ``available'' or ``required'', $-$ means ``not available''
or ``not required'', and $o$ means ``unclear''. Entries in [brackets] means
``not fully available'' or ``almost not available'', or similar.

In most cases, the \emph{versions} are those from
\texttt{snert.}\footnote{Note that for the various java lib's there's a
  little confusions concerning the numbers (and file names) as some of the
  jar files which are offered for download at
  \href{http://snert.informatik.uni-kiel.de:8080/~wprguest3/downloads/}{the
    download space of the java group} are just duplicates (with the same
  version number, sometimes different names??) of the jars, which are
  installed \emph{anyway} on snert as part of tomcat. One should base the
  tool on the \emph{official} ones, as part of the chosen tomcat
  installation. Everything else invites trouble.} Sometimes the tool
versions installed at the computer lab (or at private machines) differs,
but without much (or known) problems; even so: ultimately the
\emph{reference is snert} and there, globally installed stuff, not
something copied at some obscure private directory.


\begin{table}[htbp]
  \centering
  \small
  \input{tools}
  \caption{Tools, software, etc}
  \label{tab:tools}
\end{table}


\subsection*{External links}

\begin{itemize}
\item \href{http://java.sun.com/j2se/index.jsp}{J2SE}
\item \href{http://java.sun.com/j2ee/index.jsp}{J2EE}
\item \href{http://java.sun.com/products/ejb/}{EJB}
\item \href{http://java.sun.com/products/jsp/index.jsp}{JSP}
\item \href{http://java.sun.com/products/servlet/index.jsp}{Servelets}
\item \href{http://www.mysql.com/products/connector/j/}{JDBC}
\item \href{http://www.jboss.org/}{JBoss App. Server}
\item \href{http://subversion.tigris.org/}{Subversion}
\item \href{http://www.phpdoc.org/docs/HTMLSmartyConverter/default/phpDocumentor/tutorial_tags.pkg.html}{PhP DOC}
\item \href{http://www.pushtotest.com/}{Push2Test}
\end{itemize}




\subsection*{Alternatives}


\iffalse

        <li> 
        <li> : 500\$ the licensed version
        <li> <a href="http://borbala.com/cyberchair/">Cyberchair</a>: unknown price
        <li> <a href="http://www.ifi.uio.no/confman/ABOUT-ConfMan/">Confman</a>: Probably not (yet) very stable
        <li> <a href="http://store.lantrax.com/lantraxinc/mecoma.html">Metaframe:</a> seems to cost lots of money
      </ul>
\fi
Here's a list of available conference managers of comparable intentions.
\begin{description}
\item[\href{http://www.softconf.com/START/}{start}:] widely used
\item[\href{http://borbala.com/cyberchair/}{CyberChair:}] some well-known
  conference manager, in a free and a (more modern, more stable etc)
  licensed version. It's based on \mathit{python}
\item[\href{http://www.zakongroup.com/technology/openconf.shtml}{openconf}:]
\item[\href{http://www.paperdyne.de}{Paperdyne}:] another commercial thing
  nice demo
\end{description}



%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "main"
%%% End: 
